### 2020-06-03 writeup/experiments.tex

\textbf{MTL improves data efficiency ratio.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

@@

\textbf{Understanding MTL results via STL results.}
We show that STL results can be used to help understand MTL results
We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
The results show that STL performances are indicative of MTL performances.

>>>>

\textbf{MTL improves data efficiency ratio.}
We measure the data efficiency ratio on the sentiment analysis tasks.
In Table \ref{tab:taskonomy}, we find that by performing multi-task learning, only $39\%$ ({\cor or $36\%$?}) of the labeled data is needed to achieve comparable performance to single-task learning over all six tasks on LSTM.
The data efficiency ratio of using MLP is $100\%$ because the average performance of MTL is worse than the average of STL.
We further show that applying incremental training helps reduce the data efficiency ratio to \alert{$xx\%$}.
%If TREC is not included, we see that only $25\%$ of the labeled data is needed.

@@

\textbf{Understanding MTL results via STL results.}
We show that STL results can be used to help understand MTL results.
We validate the single-task based metric proposed in Section \ref{sec_similarity} for predicting positive or negative transfer in MTL.
Table \ref{tab:mtl_better_than_stl} shows the result on both the sentiment analysis and the ChestX-ray14 datasets.
We find that using a threshold of $\tau = 0.1$, the STL results correctly predict positive or negative transfer with $75.6\%$ accuracy and $38.8\%$ recall among 150 task pairs.
We observe similar results for 91 task pairs from the ChestX-ray14 dataset.
The results show that STL performances are indicative of MTL performances.

### 2020-06-03 writeup/related.tex

\textbf{Random matrix theory.}

>>>>

\textbf{Random matrix theory.} The random matrix theory tool and related proof of this paper fall into a paradigm of the so-called local law of random matrices \cite{erdos2017dynamical}. For a sample covariance matrix $X^\top X$ with $\Sigma=\id$, such a local law was proved in \cite{isotropic}. It was later extended to sample covariance matrices with non-identity $\Sigma$ \cite{Anisotropic}, and separable covariance matrices \cite{yang2019spiked}. On the other hand, one may derive the asymptotic result in Theorem \ref{lem_cov_shift_informal} with error $\oo(1)$ using free addition of two independent random matrices in free probability theory \cite{nica2006lectures}. To the best of my knowledge, we do not find an {\it explicit result} for the sum of two sample covariance matrices with general covariates in the literature.
